---
title: "189HW4"
author: "Shresht Venkatraman (A15910171), Kip Stopa(A15851786), Nathan Brodie(A15874575)"
date: '2023-02-10'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## CONTRIBUTIONS All 3 team members worked on each question together, and helped to format the final RMarkdown Document. Work was done in the library collectively with equal contribution from each member.

##Question 1
```{r eval=TRUE}
library(ISLR)
data(Auto)
med = median(Auto[,1])
mpgs = Auto[,1]
mpg01 = list()
for (mpg in mpgs){
  if(mpg>med){
    mpg01=append(mpg01,1)
  }
  else{
    mpg01 = append(mpg01,0)
  }
}
mpg01 = t(data.frame(mpg01))
combined = cbind(Auto,mpg01)
```

##Question 2
``` {r eval=TRUE}
for (n in 2:8){
  plot(combined[,n],combined[,10])
  boxplot(combined[,n],combined[,10])
}
```
##Of the other features in the data, we found that Weight and Horsepower seem to be the most useful in predicting mpg01. We noticed that in the scatter plots for horsepower versus mpg01 as well as weight versus mpg01, we find that there are no points in the top right of either graph. That means that high horsepower cars as well as high weight cars are very likely to fall under the median miles per gallon. We also found it interesting that there was not a strong correlation between acceleration and mpg01, and that higher acceleration cars often had an mpg over the median.

##Question 3
``` {r eval=TRUE}
train = combined[sample(nrow(combined),size=300),]
test = combined[!(row.names(combined)%in% row.names(train)),]
```

##Question 4
``` {r eval=TRUE}
library(MASS)
lda = lda(mpg01 ~ weight + horsepower,data=train)
lda
predict = predict(lda,test)$class
count = sum(data.frame(predict) != test['mpg01'])
errate = count/92
errate
```
##So we find that using the weight and horsepower as the variables that seemed the most associated, we find the error rate to be [1]

##Question 5
``` {r eval=TRUE}
qda = qda(mpg01 ~ weight + horsepower,data=train)
qda
predict2 = predict(qda,test)$class
count2 = sum(data.frame(predict2) != test['mpg01'])
errate2 = count2/92
errate2
```
##So we find that using the weight and horsepower as the variables that seemed the most associated, we find the error rate to be [1]