---
title: "HW9"
author: "Kipling Stopa A15851786, Nathan Brodie A15874575, Shrest Venkatraman A15910171"
date: '2023-03-16'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## CONTRIBUTIONS All 3 team members worked on each question together, and helped to format the final RMarkdown Document. Work was done on Zoom collectively with equal contribution from each member.

##Question 1
``` {r eval=TRUE}
x = seq(-2,2,.2)
y = 3*x + 1
y_b = -1*x/2 + 1
plot(x,y,"l",col="blue",ylab="X2",xlab="X1")
lines(x,y_b,col="red")

```
##a) The Points above the blue line represent the points for which (1 + 3X1 - X2)<0, The points below the blue line represent the points for which  (1+3X1 - X2)>0.
##b) The Points above the red line represent the points for which (-2 + X1 + 2*X2)<0, The points below the red line represent the points for which  (-2 + X1 + 2*X2)>0.

##Question 2
``` {r eval = TRUE}
##This is a circle with radius 2 centered at (-1,2)
##For some reason, the draw.circle command in R is not working correctly for us so question 2 part a) part b) were done in python, and the graph is included in the next page.

```
##Question 2 c): If the classes are defined the Red Class and the Blue Class, then (0,0) is in the blue class, (-1,1) is in the red class, and (2,2), (3,8) are in the Blue Class, The red class represents points inside our circle and the blue class represents points outside out circle.
##Question 2 d): According to slide 29 in the SVM slideshow, we know that the enlarged feature space for our equation for a circle means that X1, X1^2, X2, X2^2 are all terms of the linear decision boundary.


##Question 3
``` {r eval = TRUE}

```

